### 2013-01-26 mcmc.tex
abstract; and some outline tweaks

\begin{abstract}
    WTF is MCMC?
\end{abstract}

@@

...Search, optimization, and sampling in inference.

@@

@@

>>>>

\begin{abstract}
Markov Chain Monte Carlo (MCMC) methods for sampling probability
distribution functions, plus abundant computation, have transformed
the sciences.  Here we give a fast overview of basic MCMC methods and
then turn to practical advice for their use in real inference
problems.  We give advice on method choice, tuning for performance,
initialization and burn-in, judging convergence, and use of the chain
output to make results with error bars. [Insert some generally useful
  point here!]
\end{abstract}

@@

...Search, optimization, and sampling in inference.  MCMC does only
one of these things well!

@@

...You can't sample the likelihood!  You can only sample a posterior
pdf!

@@

...Finally, to repeat: You can't sample the likelihood!  You can only
sample a posterior pdf!
